Fictitious Play in Network Aggregative Games

### 2021-05-06 Documents/FP in NAGs/neurips_2020.tex
Updated sty file and Introduction

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2020

% ready for submission
% \usepackage{neurips_2020}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2020}

% to compile a camera-ready version, add the [final] option, e.g.:
    % \usepackage[final]{neurips_2020}

% to avoid loading the natbib package, add option nonatbib:
     \usepackage[nonatbib]{neurips_2020}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{amsmath, amsfonts, amsthm}
\usepackage{xcolor}
\usepackage{enumerate}
\usepackage{graphicx}

@@

@@

  The main contribution of this work is to study the behaviour of the Fictitious Play Learning
  Algorithm, in continuous time, when applied on a Network Aggregative Matrix Game. \fb{why FP and NAG are important?}

  We first show that a Nash Equilibrium exists and that Fictitious Play admits
  solutions in this setting. In particular, we study zero-sum games and show that
  Fictitious Play converges to a fixed point, which for a network without any
  self-loops corresponds to a Nash Equilibrium. In addition, we find that, for games
  which are not zero-sum, agents following Continuous Time Fictitious Play are able to
  achieve no regret.

  Finally, we explore the Fictitious Play algorithm through numerical simulations to understand
  how convergence rates depend on the network size and connectivity. We also show that it does not
  necessarily converge for more complex games and can, in fact, lead to more complex dynamics. In
  addition, we experiment the Fictitious Play algorithm on an agent based model for \ah{resource
  allocation?  voting?}. Finally, our experiments document how noise affects the convergence of
  fictitious play, whose theoretical analysis we point out as an interesting direction for future
  work.

  \ah{Possible additions: 1) Show that the flow is unique almost everywhere in CTFP. 2) Show the
  same results (i.e. existence and convergence) for Discrete Time Fictitious Play.}

@@

  \begin{assumption}
    \ah{I've been thinking about this a little, and I think it could be the case that
    we don't need to make this assumption at all. I will investigate this further, since I don't
    think this assumption has appeared in any of our results.} The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
    a classical assumption which is made in most game theoretic settings and includes, as a
    special case, the analysis of homogeneous agents \cite{}. However, it should be noted that,
    in \cite{Ewerhart}, CTFP was analysed without this requirement.  
  \end{assumption}

@@

    Continuing with this approach, let us look at the case where $\sum_\mu A^\mu = \textbf{0}_{n\times n}$ (i.e. a zero sum game). This means that $\sum_i u_i = 0$. Let $\xmu_\infty = \lim_{t \rightarrow \infty} \alpha^\mu(t; m)$. More specifically, $\xmu_\infty$ belongs to the set of accumulation points of $\alpha^\mu(\cdot; m)$ (which is set valued since the $BR^\mu$ map is set valued). To say that the game has `converged' we require that every $\xmu_\infty = (x^1_\infty, ... x^N_\infty)$ is an NE. \ah{I'll follow through the proof of Ewerhart for the sake of completeness: }

@@

  \subsection{Non-convergent examples}
  The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.

@@

  \begin{figure}[t]
    \centering
    \includegraphics[width = 0.7\textwidth]{Figures/convergentShapley.png}
    \caption{\label{fig::convergentShapley}}
  \end{figure}

  \begin{figure}[t]
    \centering
    \includegraphics[width = 0.7\textwidth]{Figures/nonConvergentShapley.png}
    \caption{\label{fig::nonconvergentShapley}}
  \end{figure}

@@

  \begin{figure}[t]
    \centering
    \includegraphics[width = \columnwidth]{Figures/Noise20Player.png}
    \caption{\label{fig::Noise10Player}}
  \end{figure}

  The fictitious play process in NA games requires that, at each time step, an agent takes a
  `measurement' of the aggregate strategy of its neighbours. It is on this measurement that they
  update their own strategy. It stands to reason then, that in real environments this measurement
  may be corrupted by noise. As such, we investigate the effect that introducing noise has on CTFP
  in a zero-sum NA game.

  Noisy Experiments
  \begin{enumerate}
    \item Large (p = 20) game with noise, vary the amount of noise to see at what point we break
    convergence. Main questions: \begin{itemize}
      \item At what point do we stop reaching the NE?
      \item Does it start converging to something else, or just go haywire?
      \item Would increasing the number of iterations make it converge again?
    \end{itemize}

    \item 3 Player chain. Vary the amount of noise to see the qualitative change in behaviour.
    Main questions \begin{itemize}
      \item At what point does periodic behaviour break?
      \item Do we actually always converge towards the NE?
      \item Does this happen for all periodic behaviour?
    \end{itemize}
  \end{enumerate}

>>>>

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2021

% ready for submission
\usepackage{neurips_2021}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2021}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2021}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2021}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

\usepackage{amsmath, amsfonts, amsthm}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{subcaption}

@@

Multi Agent Learning \cite{Schwartz} requires a number of agents to adapt in an environment where
each agent must adapt in response to the behaviour of the other agents. This leads to a
fundamentally non-stationary problem, which presents a challenge to designing effective learning
policies. Even when there are a small number of agents in the game, learning has been shown to lead
to non-stationary, and even chaotic behaviour \cite{SatoChaos}, and this problem becomes even more
pronounced as the number of agents increase \cite{Sanders}. In this light, it would appear that
learning when there is a large population of agents is an impossible task.

To deal with this problem, one must attempt to reduce the many player game to something which is
tractable. A number of reductions have been proposed, most notably \emph{Mean Field} Games
and \emph{Aggregative} Games. The former makes the assumption of an infinite
number of agents, so that the population can be represented through a distribution over players'
states \cite{CainesPaper} . Every agent then updates their action profiles depending on this
distribution. In the latter each agent plays considers a real valued function which is a convex
combination of the states of the other agents. In both formulations, a many player game is reduced
to the set of two player games which each agent is involved in, allowing the problem to maintain
tractability.

Whilst both formulations have shown success in multi-agent learning settings, allowing agents to
reach equilibrium strategies (c.f. \cite{MFGLearningPapers} for Mean Field Games and
\cite{Aggregative Papers} for Aggregative Games), they also present a fundamental limitation.
Namely, they both require that agents have access to the action profiles of the entire population.
This could be through communication with all other agents, or through the intervention of a central
coordinator who is able to the entire population. Whilst recent work aims to relax this assumption
through the introduction of noise \cite{MFG-FP} or partial observability \cite{AAMASPaper}, the
requirement that each agent updates their actions based on the entire population is rather strong.

In this study, we investigate a variant of the aggregative game known as the \emph{Network
Aggregative} (NA) Game. This format assumes that there is an underlying communication network
through which agents interact. Then each agent updates their actions according only to those agents
with whom they communicate. This significantly relaxes the communication load on each agent and
lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Grammatico,
LeaderFollower, MyopicAgents}. We contribute in this direction by showing that learning on an NA
game can lead to an equilibrium strategy. In particular, we analyse the Fictitious Play Learning
Algorithm \cite{Brown, Harris}, in which agents are assumed to be myopic, in that they react solely
to the previous behaviour of the others.

@@

  The main contribution of this work is to study the behaviour of the Fictitious Play (FP) learning
  algorithm, in continuous time, when applied on a Network Aggregative Matrix Game.

  We first show that a Nash Equilibrium exists and that FP admits
  solutions in this setting. In particular, we study zero-sum games and show that
  Fictitious Play converges to a fixed point, which for a network without any
  self-loops corresponds to a Nash Equilibrium. In addition, we find that, for games
  which are not zero-sum, agents following Fictitious Play are able to
  achieve no regret.

  Finally, we explore FP through numerical simulations to consider the
  question of whether it always converges. We answer this in the negative by finding a family of
  games in which action profiles cycle around the Nash Equilibrium. Finally, our experiments
  document how noise affects the convergence of Fictitious Play. Our experiments suggest that, under
  the presence of noise, the algorithm still reaches a fixed point, but perhaps not the Nash
  Equilibrium. This presents an interesting avenue for future research.

\subsection{Related Work}

\paragraph{Network Aggregative Games}

The NA game is a recent introduction \cite{Parise2015} which presents a variant of aggregative games
by adding an underlying structure to the population. Since its introduction, distributed algorithms
have been built with the aim of finding NE. In particular, \cite{Parise2015, Parise2020} consider
the case in which payoffs are given by Lipschitz functions with unique minimisers and apply standard
topological fixed point towards designing algorithms which will converge to the NE. We note that the
\emph{Mann Iteration}, one of the algorithms applied in \cite{Parise2020} shares a remarkably
similar form with the discrete variant of FP. To the best of our knowledge, this link has not been
explored in the literature and is an avenue for research which we are currently pursuing. Another
common algorithm for distributed NE seeking is the projected gradient (resp. subgradient) dynamics
which is explored in \cite{Zhang2020} (resp. \cite{Shokri2020, Shokri2021}). In all of these works,
the cost function is assumed to be convex, and therefore have a unique minimiser. In fact this is a
common assumption in works concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due to
its ubiquity in control settings. We have not yet come across works which consider NA games from the
point of view of payoff matrices, which are more common in multi agent learning settings.
Furthermore, to the best of our knowledge, this is the first work which introduces the application
of a strict learning algorithm in the NA setting.

\paragraph{Fictitious Play}

Fictitious Play was introduced by Brown in 1951 \cite{BrownPublished, BrownUnpublished} as a
'natural' way in which to approximate the Nash Equilibrium in zero sum games. It was known at the
time that a discrete variant of the algorithm would converge to the NE in two player zero-sum games
\cite{Robinson}. Since then a number of proofs of convergence were determined in 2 player games
\cite{Miyasawa, Polak, Berger, Monderer and Sela, Monderer and Shapley}, as well as corresponding
convergence rates \cite{Harris, Shapiro}. Many results hold for both the discrete and continuous
variants of FP. Their relation was finally solved by Hofbauer \cite{Hofbauer}, who showed that
attractors of the discrete time process are also attractors for the continuous time variant. As
such, most of the analysis on FP focuses on the continuous time variant \cite{Ostrovski}. It was
later shown in \cite{Shapley} that there is a family of games (now called the \emph{Shapley family})
for which FP does not converge at all but rather shows periodic behaviour. This led to research
which looks at this non convergent behaviour, specifically showing the existence of more periodic
orbits as well as chaotic behaviour \cite{Sparrow}. However, the work looking at fictitious play
where there are more than two agents is sparse. \cite{Sela} considers a game in which a multi-player
game is decomposed by requiring that each agent engage in a two person game against each of the
opponent. Their payoff is given by the sum of payoffs in all of these subgames. It was found that,
if this game is zero sum, then FP will converge. Similar results for more than two players were
found for games with identical interests in \cite{MondererShapley1994}. In \cite{FPMFG}, the action
of FP was considered in a Mean Field Game, and it was found again that the algorithm converges for
zero sum games. The most general result, and the one most similar to our own, was found by Ewerhart
and Valkanova in 2020 \cite{Ewerhart} in which they showed that fictitious play converges in network
games, where each agent is engaged in a two-player game with each of their neighbours. The rate of
convergence was found to be independent of the network size.  Our work extends the analysis of FP in
multiplayer games by considering its action in NA Games, so that the agents do not play individual
games against each of their neighbours but rather a single game against the aggregate of their
neighbours. In particular we also extend a result for two player games found by Ostrovski and van
Strein \cite{Payoff Performance} which showed that FP achieves no-regret to the multi-player
setting.

@@

  \begin{assumption}
    The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
    a classical assumption which is made in most game theoretic settings and includes, as a
    special case, the analysis of homogeneous agents \cite{}. However, it should be noted that,
    in \cite{Ewerhart}, CTFP was analysed without this requirement.  
  \end{assumption}

@@

    Continuing with this approach, let us look at the case where $\sum_\mu A^\mu =
    \textbf{0}_{n\times n}$ (i.e. a zero sum game). This means that $\sum_i u_i = 0$. Let
    $\xmu_\infty = \lim_{t \rightarrow \infty} \alpha^\mu(t; m)$. More specifically, $\xmu_\infty$
    belongs to the set of accumulation points of $\alpha^\mu(\cdot; m)$ (which is set valued since
    the $BR^\mu$ map is set valued). To say that the game has `converged' we require that every
    $\xmu_\infty = (x^1_\infty, ... x^N_\infty)$ is an NE. Under these conditions, we may adapt the
    techniques of (\cite{Ewerhart} Prop. 1) to show convergence.

@@

  \subsection{Non-convergent examples} \label{sec::NonConv}
  The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.

@@

  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.4 \textwidth}
      \includegraphics[width = \textwidth]{Figures/convergentShapley.png}
    \caption{\label{fig::convergentShapley}}
    \end{subfigure}
    \begin{subfigure}[b]{0.4 \textwidth}
      \includegraphics[width = \textwidth]{Figures/nonConvergentShapley.png}
      \caption{\label{fig::nonconvergentShapley}}
    \end{subfigure}
    \caption{\label{fig::Shapley}}
  \end{figure}

  \begin{figure}[t]
    \centering
    \includegraphics[width = 0.7 \textwidth]{Figures/3PlayerChainNoNoise.png}
    \caption{\label{fig::3PlayerChainNoNoise}}
  \end{figure}

@@

  \begin{figure}[t]
    \centering
    \includegraphics[width = \columnwidth]{Figures/Noise20Player.png}
    \caption{\label{fig::Noise20Player}}
  \end{figure}

  \begin{figure}[t]
    \centering
    \includegraphics[width = \columnwidth]{Figures/3PlayerChainNoise.png}
    \caption{\label{fig::3PlayerChainNoise}}
  \end{figure}

  The fictitious play process in NA games requires that, at each time step, an agent takes a
  `measurement' of the aggregate strategy of its neighbours. It is on this measurement that they
  update their own strategy. It stands to reason then, that in real environments this measurement
  may be corrupted by noise.

  As such, we investigate the effect that introducing additive noise has
  on CTFP in a zero-sum NA game. We do this in the following manner: at each time step, the
  reference signal $\refmu(t)$ is adjusted to $\refmu + \gamma \xi$ where $\xi$ is drawn from the
  standard normal distribution (zero mean and unit variance). By varying $\gamma$, we vary the
  strength of the noise. We vary $\gamma$ up to $0.5$ since, above this value, noisy measurements
  are likely to lie outside of the simplex. Since $\refmu$ is constrained to lie within $\Delta$, we
  can consider the range $\gamma \in [0, 0.5]$ to be the \emph{physical region}, in which noise is meaningful.

  In Figure \ref{fig::Noise10Player}, we consider a zero-sum NA game with 10 players. When there is
  no noise, it can be seen that FP reaches a fixed point which, since we set $w^{\mu \mu} = 0$,
  corresponds to an NE. After increasing $\gamma$, however, we find that the agents no longer
  converge to this NE, but rather shift away from it. What is interesting, however, is that the
  orbits do still reach a stationary state in the long run which suggests that FP is still able to
  converge with the introduction of noise. Figure \ref{fig::Noise20Player} shows similar behaviour
  for $N = 20$, and in our experiments we found this to be ubiquitous regardless of the choice of
  $N$ or $n$.

  In Figure \ref{fig::3PlayerChainNoise} we revisit the Three Player Chain of Section
  \ref{sec::NonConv}, now under the influence of additive noise. For the sake of brevity, we only
  display the distance to the Nash Equilibrium of the first player's action, since the other agents
  behave in the same way. It can be seen that a small amount of noise has the effect of decreasing
  the size of the periodic orbit (c.f. Figure \ref{fig::3PlayerChainNoNoise}). However, as $\gamma$
  is increased to $0.5$, the algorithm seems to exhibit convergence to the NE. The implication is
  that the addition of noise may cause periodic behaviour to break and lead to the Nash Equilibrium.
  An interesting point to note is that this behaviour is in stark contrast to the replicator
  dynamic (RD) \cite{Maynard-Smith}, another adaptive algorithm linked to multi agent learning
  \cite{CyclesAdversarialLearning}. In \cite{Imhof} and \cite{Galla}, it was found that the
  introduction of random mutations can remove convergent behaviour and instead lead to periodicity.
